The imprint of global magma oceans on exoplanet demographics

### 2023-01-19 src/tex/ms.tex
create combined figure exploring sample size and FGK vs. M.

    \begin{figure}[ht!]
%    \script{figurescript.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/plato_fgrid.pdf}
            \caption{
            Expected evidences as a function of the fraction of planets harboring runaway greenhouse climates for different versions of the \plato\ survey.
            $\Delta \ln Z > 3$ (gray horizontal line) is considered sufficient evidence to reject the null hypothesis.
            For a large planet yield of $N = \var{Nplato}$, even small planet fractions $\gtrsim \var{platoMinfrgh}$ allow a detection.
                A much smaller sample of 100 planets is sufficient if their masses are constrained to within \SI{10}{\percent} (dashed green line).
                Without such follow-up measurements, sufficient diagnostic power can only be achieved with this sample if $f_\mathrm{rgh} \gtrsim \var{platoMinfrghHundred}$.
               Even smaller samples are unlikely to yield a significant detection.
            }
            \label{fig:plato_fgrid}
        \end{centering}
    \end{figure}

@@

\subsection{Mission design trades}\label{sec:mission-design-trades}
We now turn to mission design trades that influence the statistical power for testing the runaway greenhouse hypothesis.
...

>>>>

    \begin{figure*}[ht!]
%    \script{figurescript.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/plato_fgrid.pdf}
            \caption{
            Expected evidences as a function of the fraction of planets harboring runaway greenhouse climates for different versions of the \plato\ survey.
            $\Delta \ln Z > 3$ (gray horizontal line) is considered sufficient evidence to reject the null hypothesis.
            \textit{Left:} For a large planet yield of $N = \var{Nplato}$, even small planet fractions $\gtrsim \var{platoMinfrgh}$ allow a detection.
                A much smaller sample of 100 planets is sufficient if their masses are constrained to within \SI{10}{\percent} (dashed green line).
                Without such follow-up measurements, sufficient diagnostic power can only be achieved with this sample if $f_\mathrm{rgh} \gtrsim \var{platoMinfrghHundred}$.
               Even smaller samples are unlikely to yield a significant detection.
            \textit{Right:} Evidences when only FGK or only M~dwarfs are considered.
                Only M~dwarfs host enough planets on both sides of the threshold instellation to allow a detection of the runaway greenhouse signal.
            }
            \label{fig:plato_fgrid}
        \end{centering}
    \end{figure*}

@@

\subsection{Mission design trades}\label{sec:mission-design-trades}
We now turn to mission design trades that influence the statistical power for testing the runaway greenhouse hypothesis.
...
\begin{note}
...FOLLOW-UP...

The advantage of mass measurements for the planet sample can be enhanced with a wise selection of follow-up targets, i.e. favoring those planets residing close to $S_\mathrm{thresh}$.
\end{note}
